Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-09 draft.tex
change a couple of words in abstract
add SlimFly citation

The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers. Preliminary studies show that random placement with adaptive routing should be the rule of thumb to utilize such networks, since random placement with adaptive routing can uniformly distribute traffic over the network and alleviate congestion. However, in this paper, we made the observation that while random placement coupled with adaptive routing can load-balance the network when multiple jobs are running concurrently, they can not guarantee the best performance for each single job. The performance improvement of communication-intensive jobs comes with the sacrifice of less intensive jobs. We refer this phenomenon as ``bully" between concurrently running jobs. We presented a detailed analysis about this ``bully" behavior between jobs at the network level based on a sophisticated, high-fidelity discrete even-driven simulation tool. The observations and analysis presented in this work illuminate a path to the adoption of more efficient job placement policy and routing algorithm for HPC systems with dragonfly network.

>>>>

The high-radix, low-diameter dragonfly network will be the choice of many computing facilities for building their next generation supercomputers. 
Preliminary studies show that random job placement with adaptive routing should be the rule of thumb to utilize such networks for it can uniformly distribute traffic and alleviate congestion. 
However, in this paper, we made the observation that while random job placement coupled with adaptive routing can load-balance the network, it can not guarantee the best performance for every single job.
The performance improvement of communication-intensive applications comes at the expense of performance degradation of less intensive ones. 
We identify this ``bully" behavior and validate its underneath causes with the help of detailed network simulation and real application traces.
We investigate a hybrid job placement policy as an alternative for dragonfly connected systems.
Initial experimentation shows that hybrid job placement aids in reducing the worst-case performance degradation for less communication-intensive applications while retaining the performance of communication-intensive ones.

### 2016-04-09 methodology.tex
move the 2nd paragraph in Section3.4 to section3.3
add SlimFly citation

We utilize the CODES simulation toolkit (Co-Design of Multilayer Exascale Storage Architectures)~\cite{misbah-tpds}, which builds upon the ROSS parallel discrete event simulator~\cite{carothers_ross:_2002,barnes_warp_2013} to enable exploratory study of large scale systems of interest to the HPC community. CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and fat-tree~\cite{ning-pads-2015} networks with packet-level high-fidelity simulation. It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI trace library available as part of the SST macro toolkit~\cite{sst}. 
The behavior and performance of CODES dragonfly network model has been validated by Mubarak et al.\ \cite{codes-dragonfly} against booksim, a serial cycle-accurate interconnection network simulator~\cite{booksim-simulator}.

@@

Note that we do not model computation for each MPI rank due to both the complexities inherent in performance prediction on separate parallel architectures as well as the emphasis on the side of the Design Forward traces on communication behavior rather than compute representation; users are instructed to treat the traces as if they came from one MPI rank-per-node configuration, despite being gathered using a rank-per-core approach. 
%We instead allow MPI communications to proceed as quickly as they are able. 
%\TODO{is this a good enough explanation? Anything else we should add?}

@@

Each rank of each application is run on a dedicated node, following the recommended interpretation of the traces by the Design Forward team.

>>>>

We utilize the CODES simulation toolkit (Co-Design of Multilayer Exascale Storage Architectures)~\cite{misbah-tpds}, which builds upon the ROSS parallel discrete event simulator~\cite{carothers_ross:_2002,barnes_warp_2013} to enable exploratory study of large scale systems of interest to the HPC community. CODES supports dragonfly~\cite{codes-dragonfly, misbah-tpds}, torus~\cite{misbah-pads-2014, ning-pads-2011}, and Slim Fly~\cite{wolfe-pads-2016} networks with flit-level high-fidelity simulation. It can drive these models through an MPI simulation layer utilizing traces generated by the DUMPI MPI trace library available as part of the SST macro toolkit~\cite{sst}. 
The behavior and performance of CODES dragonfly network model has been validated by Mubarak et al.\ \cite{codes-dragonfly} against booksim, a serial cycle-accurate interconnection network simulator~\cite{booksim-simulator}.

@@

Note that we do not model computation for each MPI rank due to both the complexities inherent in performance prediction on separate parallel architectures as well as the emphasis on the side of the Design Forward traces on communication behavior rather than compute representation; users are instructed to treat the traces as if they came from one MPI rank-per-node configuration, despite being gathered using a rank-per-core approach. We follow the recommended interpretation in our simulations. 
%We instead allow MPI communications to proceed as quickly as they are able. 
%\TODO{is this a good enough explanation? Anything else we should add?}

@@
